---
title: "432 Week 4 assignment"
author: "Maya Dixon"
date: "03/02/2021"
output: html_document
---

# Part 1: Data Science 

#### 1. Open the project folder used in last week’s tutorial and ensure that it is properly synced with GitHub

#### 2. Create a new R Markdown file called Regex.Rmd


a. Import your measurements.csv file from the Week 1 Assignment into an object called MData

```{r}
library(dplyr)
setwd("~/Desktop/SCHOOL/BIOL 432")
MData <- read.csv("./measurements.csv")
str(MData)
```

b. Use a dplyr command AND regular expression(s) to add a new column called Sp that shortens the genus name in the Organism column to only the first letter and period. For example: Homo sapiens in the original Organism column becomes H. sapiens in the Sp column.

```{r}
MData <- MData %>% #Assignment the changes to the variable so it's saved
  mutate(Sp = sub("(\\w)\\w+","\\1.",Organism))

# the sub function is a regular expression that allows you to substitute a word, letter or value in your Species with whatever is specified in the second slot. The "(\\w)" captures the entire word and the "\\w+" that follows indicates to replace the whole word. In the second slot the "\\1." tells it to replace the first word with the first letter followed by "."). 

# Making sure the data looks correct
print(MData)
```

c. Use a dplyr command to create a new dataset BUT with Sp column instead of the Organism column, moved to the beginning in place of the original Organism column.

```{r}
MeasShort <- MData %>% 
  select(Sp, everything(), -Organism)
# Saving the data to a new variable entitled MeasShort

print(MeasShort)
```

```{r}
write.csv(MeasShort, "~/Desktop/SCHOOL/BIOL 432/MeasShort.csv")
```


 
# Part 2: Bash 

#### 1. Inside your project folder, write a bash script called MyCount.sh that will loop through a sequence of 20 numbers. In each iteration the script will print out the number of the loop iteration AND whether it is a single- or double-digit number. For example, some of the output should look like this:
8 is a single-digit number
9 is a single-digit number
10 is a double-digit number
11 is a double-digit number

#!/bin/bash

# 432 Assignment 4


for Count in {1..20}
do 
if [ $Count -lt 10 ]; then 
	echo "$Count is a single-digit number"
elif [ $Count -gt 9 ]; then
	echo "$Count is a double-digit number"
fi
done























































