---
title: "Week 6 assignment"
output: html_notebook
---

```{r}
library(ape)
library(sangerseqR)
library(ggplot2)
```


```{r}
library(BiocManager)
install(c("genbankr", "Biostrings", "ggtree", "annotate"))
```

```{r}
install.packages(c("reshape2", "rentrez"))
library(rentrez)
library(reshape2)
```

```{r}
install.packages("seqinr")
library(seqinr)
```


The sequence was saved as a fasta file which has the header as the first line and the sequence as the second line. 

```{r}
human_seq <- read.fasta("~/Desktop/SCHOOL/BIOL 432/Human isolate.fa", as.string = T) #read the fasta file from folder
human_seq
```

```{r}
library(annotate)
hsBLAST<-blastSequences(human_seq, as = 'data.frame',
                           hitListSize = 100, timeout = 1200)
#this step is using BLAST to pull similar sequences from genbank.
```

```{r}
hsHitsDF<-data.frame(ID=hsBLAST$Hit_accession,Seq=hsBLAST$Hsp_hseq,
                     stringsAsFactors = FALSE)
# here we are making a simple vector into a simple data.frame object with two columns
```

```{r}
hsBLAST$Hit_len
# This helps us visualize the length of the sequences
```

```{r}
hsHitsDNA<-sapply(hsHitsDF$Seq,strsplit,split="")
# this splits the DNA sequence for each row in a single line of code
```

```{r}
names(hsHitsDNA)<-paste(1:nrow(hsHitsDF),hsHitsDF$ID,sep="_") 
# Giving each sequence a unique name
```

```{r}
hsHitsDNA<-as.DNAbin(hsHitsDNA) 
# Convert to a DNAbin object
```

```{r}
hsAlign<-muscle(hsHitsDNA,quiet=F)
# Using muscle on our DNAbin object
```

```{r}
checkAlignment(hsAlign[1:20,1:100],what=1)
# Inspecting the alignments for any errors
```

```{r}
checkAlignment(hsAlign[21:40,1:100],what=1)
```

```{r}
checkAlignment(hsAlign,what=2)
```

```{r}
checkAlignment(hsAlign,what=3)
# Here we are checking the aligned for the sequences and they are all aligned which is why there is a lign as the graph.
```

```{r}
checkAlignment(hsAlign,what=4)
```

```{r}
KeepSeq<-SeqLen>1000
hsSubset<-hsAlign[KeepSeq,]
hsAlign<-muscle(hsSubset,quiet=F)
```


```{r}
hsDM<-dist.dna(hsAlign, model="K80")
class(hsDM)
```

```{r}
length(hsDM)
```

```{r}
hsDMmat<-as.matrix(hsDM)
dim(hsDMmat)
```

```{r}
View(hsDMmat)
```

```{r}
Dat<-melt(hsDMmat)
dim(Dat)
```

```{r}
ggplot(data = Dat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```

```{r}
ggplot(data = Dat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()+scale_fill_gradientn(colours=c("white","blue","green","red"))
```

These graphs make sense because all our sequences are aligned

```{r}
hsTree<-nj(hsDM)
str(hsTree)
```

```{r}
class(hsTree)
```

```{r}
library(ggtree)
```

```{r}
ggtree(hsTree)
```

When the ID's were put into the BLAST search the results came up with Severe acute respiratory syndrome coronavirus 2 isolate which is COVID in humans. So this sequence belongs to the COVID 2 virus which was isolated from the patients biofluid's this is something to be very concerned about. 






















